Example of Market Simulator Dasbhaord

### 2021-09-22 README.Rmd
Add note about RStudio terminal

```sh
# On macOS
cd path/to/this/project
xattr -w com.dropbox.ignored 1 data/raw_data/posterior_draws

# On Windows (with PowerShell)
cd path/to/this/project
Set-Content -Path 'data/raw_data/posterior_draws' -Stream com.dropbox.ignored -Value 1
```

>>>>

```sh
# On macOS
cd path/to/this/project  # Not needed if you use the terminal panel in RStudio after opening the project
xattr -w com.dropbox.ignored 1 data/raw_data/posterior_draws

# On Windows (with PowerShell)
cd path/to/this/project  # Not needed if you use the terminal panel in RStudio after opening the project
Set-Content -Path 'data/raw_data/posterior_draws' -Stream com.dropbox.ignored -Value 1
```
